Meta-analytic evidence that sexual selection improves population fitness

### 2019-03-28 meta_analysis_sexual_selection_pop_fitness.Rmd
Source data title

**Source Data:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
 <br/><br/> 
```{r}
# Load the data and format the variables
full_dataset <- read.csv('data/meta_analysis_dataset.csv') %>%
  mutate(Study.ID = factor(Study.ID),
         Group.ID = factor(Group.ID),
         Environment = relevel(factor(Environment), ref = "Unstressed"),
         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"),
         Pre.cop = relevel(factor(Pre.cop), ref = "0"),
         Post.cop = relevel(factor(Post.cop), ref = "0"),
         Blinding = factor(Blinding))

>>>>

**Source Data** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.

```{r}
# Load the data and format the variables
full_dataset <- read.csv('data/meta_analysis_dataset.csv') %>%
  mutate(Study.ID = factor(Study.ID),
         Group.ID = factor(Group.ID),
         Environment = relevel(factor(Environment), ref = "Unstressed"),
         Outcome.Class = relevel(factor(Outcome.Class), ref = "Indirect"),
         Pre.cop = relevel(factor(Pre.cop), ref = "0"),
         Post.cop = relevel(factor(Post.cop), ref = "0"),
         Blinding = factor(Blinding))
